---
title: "Basic_stats"
author: "lushi"
date: "26/03/2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(ggplot2)
library(plotly)
library(ggpubr)
require(reshape2)
library(plyr)
library(Hmisc)
library(tidyverse)
library(stargazer)
```

#This file shows the basic demographic information from the annotated users (N= 77)

Id80PerRetained.csv userid with more than 80% posts retained (we removed posts with foreign language that we can't understand)
We have 70 participants in total after removing them 
Continous variables
Note: posts count and day spread in here is from the whole sample. Not our subset sample.
```{r pressure, echo=FALSE}
# setwd('/Users/lucia/phd_work/cognitive_distortion/') 
setwd('/home/lucia/phd_work/mypersonality_data/cognitive_distortion/') 
# '/home/lucia/phd_work/mypersonality_data/cognitive_distortion/'
allData <- read.csv('data/important_data/user_scale_post_time2.csv')
allData <- subset(allData, age > 17 | is.na(age))
#merge with annotated users
users <- read.csv('data/important_data/twoM_newLabels80P.csv')
users <- users[!duplicated(users$userid), ]
users <- users$userid
AnnotatedUsersInf <- allData[allData$userid %in% users,]
#select continous values
SelData <- AnnotatedUsersInf[, c(5:6, 14, 24, 26:30, 36:37)]
#summa <- summary(SelData)
#summa[1:5,]
#stargazer(summa[1:2,],type = "html", summary = FALSE, rownames = FALSE)
data <- AnnotatedUsersInf[, c('userid','CESD_sum', 'swl')]
#write.csv(data, '/Users/lucia/phd_work/cognitive_distortion/data/important_data/FinalSampleUsers.csv')

stargazer(SelData)


```






Check skewness of variables
```{r }
shapiro.test(AnnotatedUsersInf$ope)
shapiro.test(AnnotatedUsersInf$agr)
shapiro.test(AnnotatedUsersInf$ext)
shapiro.test(AnnotatedUsersInf$con)
shapiro.test(AnnotatedUsersInf$neu)
shapiro.test(AnnotatedUsersInf$swl)
shapiro.test(AnnotatedUsersInf$network_size)
shapiro.test(AnnotatedUsersInf$CESD_sum)

plot(density(AnnotatedUsersInf$ope)) # peaks at around 4 and 4.6
plot(density(AnnotatedUsersInf$swl)) # peaks at around 3 and 4.5
```
CESD cutoff 21 
```{r}
high <- SelData[SelData$CESD_sum > 21,]
low <- SelData[SelData$CESD_sum <= 21,]

high$group <- 1
low$group <- 2
both <- rbind(high,low)

stargazer(high, digits = 2, omit.summary.stat = c("min","max","n"))
stargazer(low, digits = 2, omit.summary.stat = c("min","max","n"))

wilcox.test(swl ~ both$group, data = both)
wilcox.test(ope ~ both$group, data = both)
wilcox.test(agr ~ both$group, data = both)
wilcox.test(neu ~ both$group, data = both)
wilcox.test(con ~ both$group, data = both)
wilcox.test(ext ~ both$group, data = both)



```

get gaussian
```{r}
sd(SelData$CESD_sum)
p <- ggplot(SelData) +
    geom_density(aes(x=CESD_sum), fill="#ADD8E6", size=1) +
    labs(title="CESD Score") +
    theme(text = element_text(size=20))+
    xlim(-10,60) +
    xlab("Normal Dist. mean=23.79, sd=12") +
    ylab("Density") +
    geom_vline(xintercept=22, linetype="longdash", colour="red") +
    annotate("text", x=0, y=0.02, label= "low score", size = 6) +
    annotate("text", x = 50, y=0.02, label= "high score", size = 6) 
p
#stat_function(fun = dnorm, args = list(mean = mean(SelData$CESD_sum), sd = sd(SelData$CESD_sum)))

```

get gaussian, other variables
```{r}
SelData$group <- 'whole_sample'
high$group <- 'high_CESD'
low$group <- 'low_CESD'

plot_density_data <- function(SelData, high, low, var){
  swl_whole <- SelData[,c(var,'group')]
  swl_high <- high[,c(var,'group')]
  swl_low <- low[,c(var,'group')]
  swl_data <- rbind(swl_low, swl_high)
  swl_data <- rbind(swl_whole, swl_data)
  return (swl_data)
}
  

  # Overlaid histograms with means
plot_density <- function(var, plot_density_data, var_mean, title, x_axis_start, x_axis_end){
  p <- ggplot(plot_density_data, aes(x=var, color=group)) +
      xlim(x_axis_start, x_axis_end) +
      labs(title=title) + 
      geom_density( alpha=.5, position="identity") +
      theme(axis.text.x = element_text(size=15), axis.text.y = element_text(size=15),
            axis.title.x = element_blank())+
      geom_vline(data=var_mean, aes(xintercept=var.mean,  colour=group),
                 linetype="dashed", size=1)
  
  return (p)
}


data <- plot_density_data(SelData, high, low, 'swl')
var_mean <- ddply(data, "group", summarise, var.mean=mean(swl))
swl_plot <- plot_density(data$swl, data, var_mean, 'SWL', -1, 9)
swl_plot

data <- plot_density_data(SelData, high, low, 'ope')
var_mean <- ddply(data, "group", summarise, var.mean=mean(ope))
ope_plot <- plot_density( data$ope, data, var_mean, 'openness', 2, 6)
ope_plot 

data <- plot_density_data(SelData, high, low, 'con')
var_mean <- ddply(data, "group", summarise, var.mean=mean(con))
con_plot <- plot_density(data$con, data, var_mean, 'conscientiousness', 0, 6)
con_plot

data <- plot_density_data(SelData, high, low, 'ext')
var_mean <- ddply(data, "group", summarise, var.mean=mean(ext))
ext_plot <- plot_density(data$ext, data, var_mean, 'extroversion', 0, 6)
ext_plot 

data <- plot_density_data(SelData, high, low, 'agr')
var_mean <- ddply(data, "group", summarise, var.mean=mean(agr))
agr_plot <- plot_density(data$agr, data, var_mean, 'agreeableness', 2, 6)
agr_plot

data <- plot_density_data(SelData, high, low, 'neu')
var_mean <- ddply(data, "group", summarise, var.mean=mean(neu))
neu_plot <- plot_density(data$neu, data, var_mean, 'neuroticism', 0, 6)
neu_plot

ggarrange(ope_plot, con_plot, ext_plot, agr_plot, neu_plot, swl_plot,
          labels = c("A", "B", "C",  "D", "E", "F"),
          ncol = 2, nrow = 3, common.legend = TRUE)
```


get boxplot#
```{r}
get_personality_plot <- function(personality_matrix, title){
  plotVar <- gather(personality_matrix, personality_dimentions)
  plotVar$personality_dimentions <- factor(plotVar$personality_dimentions)
  
  p1 <- ggplot(plotVar, aes(x=personality_dimentions, y=value, fill = personality_dimentions)) + geom_boxplot() +
    ylab('score')+
    ggtitle(title)+
      guides(fill=FALSE) + coord_flip()
  #p1 <- ggplotly(p1)
  return (p1)
}

p1  <- get_personality_plot(SelData[5:10], 'Personality score from whole sample')
p2  <- get_personality_plot(high[5:10], 'Personality score from high group')
p3  <- get_personality_plot(low[5:10], 'Personality score from low group')




ggarrange(p1, p2, p3,
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 3)
```



```{r }
p1  <- boxplot(SelData[, c(1:2, 4)], data=SelData, main="Demographic Informtation", names=names(SelData[, c(1:2, 4)]))
p2 <- boxplot(SelData[, c(3, 11)], data=SelData, main="Demographic Informtation", names=names(SelData[, c(3, 11)]))
p3 <- boxplot(SelData[, c(5:9)], data=SelData, main="Demographic Informtation", names=names(SelData[, c(5:9)]))
```

Categorical variables
Percentage of people in specific demographic groups
The acronyms are standard locale / language acronyms.

```{r }
SelDataCat <- AnnotatedUsersInf[, c(9:10, 12, 23)]
prop.table(table(SelDataCat$marital_status))
prop.table(table(SelDataCat$ethnicity))
prop.table(table(SelDataCat$gender))
prop.table(table(SelDataCat$locale))
```

gender female = 1, male = 0
```{r }
# cut off score as 16
print('16 cutoff')
table(AnnotatedUsersInf$gender, AnnotatedUsersInf$CESD_sum > 16)
print('21 cutoff')
table(AnnotatedUsersInf$gender, AnnotatedUsersInf$CESD_sum > 21)
print('16 cutoff')
table(AnnotatedUsersInf$ethnicity, AnnotatedUsersInf$CESD_sum > 16)
print('21 cutoff')
table(AnnotatedUsersInf$ethnicity, AnnotatedUsersInf$CESD_sum > 21)
print('16 cutoff')
table(AnnotatedUsersInf$marital_status, AnnotatedUsersInf$CESD_sum > 16)
print('21 cutoff')
table(AnnotatedUsersInf$marital_status, AnnotatedUsersInf$CESD_sum > 21)

```

heatmap
```{r}
 get_lower_tri<-function(cormat){
    cormat[upper.tri(cormat)] <- NA
    return(cormat)
  }

get_melted <- function(data){
  cormat <- round(rcorr(as.matrix(SelData[5:11][sapply(SelData[5:11],is.numeric)]))$r,2)
 # cormat <- round(cor(data),2)
  upper_cormat <- get_lower_tri(cormat)
  melted_cormat <- melt(upper_cormat, na.rm = TRUE)
  return(melted_cormat)
}

get_melted_p <- function(data){
  cormat.p <-  round(rcorr(as.matrix(SelData[5:11][sapply(SelData[5:11],is.numeric)]))$P, 3)
 # cormat <- round(cor(data),2)
  upper_cormat <- get_lower_tri(cormat.p)
  melted_cormat <- melt(upper_cormat, na.rm = TRUE)
  return(melted_cormat)
}
  
get_cor_plot <- function(melted_cormat){
    plot<- ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
    geom_tile()+
     scale_fill_gradient2(low = "#F1D302", high = "#235789", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
   theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 16, hjust = 1), axis.text.y = element_text(vjust = 1, 
    size = 16, hjust = 1), axis.title.x = element_blank(), axis.title.y = element_blank(), legend.justification = c(1, 0), legend.position = c(0.4, 0.7), legend.direction = "horizontal") +
    geom_text(aes(Var1, Var2, label = value), color = "black", size = 7) +
    geom_text(aes(label = pvalue), color = "black", size = 5, vjust = 2)
     
  return (plot)
}

recode_p <- function(p_value){
  p_value[p_value <= 0.05] <- "*"
  p_value[p_value <= 0.01] <- "**"
  p_value[p_value <= 0.001] <- "***"
  p_value[p_value > 0.05] <- " "
  return (p_value)
}

melted <- get_melted(SelData[5:11])
melted_p <- get_melted_p(SelData[5:11])
melted_combine <- merge(melted, melted_p, by = c('Var1', 'Var2'))
colnames(melted_combine) <- c('Var1', 'Var2', 'value','pvalue') 


melted_combine$pvalue <- recode_p(melted_combine$pvalue)
get_cor_plot(melted_combine)


```
