---
title: "statsForMoodVec"
author: "Lushi Chen"
date: "24 January 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(progress = TRUE, verbose = TRUE)
```

## here we check how many posts were removed in each user (foreign language), remove participants who have more than 80% of posts removed
52 participants here have all their posts retained, 16 participants have less than 10% of posts removed, 6 have 10% - 40% of posts removed, 3 have more than 80% posts removed

Here we remove participants with 80% of the posts removed. The rest of the participants have 55.93 posts in average in 60 days. For number of empty days per user, see ValenceVector.ipynb

```{r }
#data remove noise
cleanData <- read.csv("~/phd_work/mypersonality_data/cognitive_distortion/database/twoM_database.csv", header = T, fill=TRUE,row.names=NULL)
#all data
AllData <- read.csv("~/phd_work/mypersonality_data/cognitive_distortion/database/twoMonthsAnno.csv", header = T, fill=TRUE,row.names=NULL)
#count number of posts per user
cleanCount <- data.frame(table(cleanData$userid))
names(cleanCount) <- c('userid','cleanCount')
noiseCount <- data.frame(table(AllData$userid_y))
names(noiseCount) <- c('userid','noiseCount')
counts <- merge(cleanCount, noiseCount, by = 'userid')
#percentatage of posts being removed
counts$removePer <- 1 - (counts$cleanCount/counts$noiseCount)
#partipants have how many posts removed?
c <- counts[counts$removePer < 0.00001,]
length(c$userid)

c2 <- counts[counts$removePer < 0.1 & counts$removePer > 0,]
length(c2$userid)

c3 <- counts[counts$removePer < 0.4 & counts$removePer > 0.1,]
length(c3$userid)

c4 <- counts[counts$removePer > 0.8,]
length(c4$userid)

#remove participants with less than 80% of posts removed
data <- counts[counts$removePer < 0.8,]
summary(data)

write.csv(data, '~/phd_work/mypersonality_data/cognitive_distortion/important_data/Id80PerRetained.csv')
```

