---
title: "Basic_stats"
author: "Lushi Chen"
date: "3 October 2018"
output: html_document
---

```{r setup, include=FALSE}
require(dplyr)
require(tidyverse)
require(effsize)
require(moments)
```

## R Markdown
resample_5000 is the label file of the sample. The sample is selected with sampling_strategy.Rmd
variables in the file include 
text, negative_emo, distortion(boolean), repost(boolean), negative_thinking(boolean), post_time, time_diff
time_diff: 

scale files include: userid,ethnicity,marital_status, parents_together, gender, age, relationship_status, timezone, ope, con, ext, agr, neu, swl, CESD_sum, conformity,tradition, benevolence, universalism, self_direction, stimulation, hedonism, achievement, power

```{r cars}
#set working directory 
setwd('~/phd_work/mypersonality_data/cognitive_distortion/')

labels <- read.csv("./data/resample_5000.csv", header = T, fill=TRUE,row.names=NULL) %>%
  dplyr::select(userid, text, negative_emo, distortion, repost, negative_thinking, post_time, time_diff)

scales <-  read.csv("./data/user_scale_post_time2.csv", header = T, fill=TRUE,row.names=NULL) %>%
  dplyr::select(userid,ethnicity,marital_status, parents_together, gender, age, relationship_status, timezone, ope, con, ext, agr, neu, swl, CESD_sum, conformity,tradition, benevolence, universalism, self_direction, stimulation, hedonism, achievement, power)

```

merge scales with label file 
```{r pressure, echo=FALSE}
#merge scales and compute the number of posts in each user in the select sample
label_scale <- merge(labels, scales, by = 'userid')
post_count <- aggregate(data.frame(count = label_scale$userid), list(value = label_scale$userid), length)
colnames(post_count) <- c('userid','post_count')

label_scale2 <- merge(post_count, label_scale, by = 'userid')
#label_scale2 <- subset(label_scale2, label_scale2$post_count >=20)
```

Is there negative emotion from the author ?  (1: Yes, 2:No, 3: Mixed)
Label Cognitive Distortion (1: Yes, 2:No)
Here we aggregate the negative emotion
(Must convert negative emotion as boolean then do correlation, recode this part)

```{r negative emotion}
#solution 1: convert mixed emotion to 1
label_scale2$negative_emo[label_scale2$negative_emo==3] <- 1
#count the number of posts with negative emotion in each user

neg_emo_score <- aggregate(data.frame(neg_emo_score = label_scale2$negative_emo == 1), list(userid = label_scale2$userid), sum)

#normalize the negative emotion score by number of posts
label_emo <- merge(neg_emo_score, label_scale2, by = 'userid')
label_emo$negative_emo_score2  <- label_emo$neg_emo_score/label_emo$post_count

# mixed of positive and negative emotion
#neg_emo_score_m <- aggregate(data.frame(neg_emo_score = label_scale2$negative_emo == 3), list(userid = label_scale2$userid), sum)

#neg_emo_score <- merge(neg_emo_score, neg_emo_score_m, by = 'userid') 
#colnames(neg_emo_score) <- c('userid', 'neg','mix')

##adding up negative emotion score and mixed score? doesn't make sense
#neg_emo_score$negative_score <- neg_emo_score$neg + neg_emo_score$mix
```

```{r}
#solution 2: convert mixed emotion to 1
label_scale2 <- merge(post_count, label_scale, by = 'userid')
label_scale2$negative_emo[label_scale2$negative_emo==3] <- 2

#count the number of posts with negative emotion in each user

neg_emo_score_s2 <- aggregate(data.frame(neg_emo_score = label_scale2$negative_emo == 1), list(userid = label_scale2$userid), sum)

#normalize the negative emotion score by number of posts
label_emo_s2 <- merge(neg_emo_score_s2, label_emo, by = 'userid')
label_emo_s2$negative_emo_score_s2  <- label_emo$neg_emo_score/label_emo$post_count

```

recode this part
count the number of negative emotion posts in each user then do correlation
compute correlation between 
1. negative emotion and CESD
2. negatibe emotion and SWL


```{r}
#remove duplicate then compute correlation
label_emo2 <- label_emo[!duplicated(label_emo$userid),]
#1. per post level negative emotion and CESD
cor.test(label_emo2$negative_emo_score2, label_emo2$CESD_sum)
#0.1232792   p-value = 0.2854
cor.test(label_emo2$negative_emo_score_s2, label_emo2$CESD_sum)
# 0.203759  p-value < 2.2e-16

# 2. per post level negative emotion and SWL
cor.test(label_emo2$negative_emo_score2, label_emo2$swl)

# 3. per day negative emotion and SWL
cor.test(label_emo2$negative_score, label_emo2$CESD_sum)
#0.192121 p-value = 0.09415
mean(label_emo2$negative_score)
sd(label_emo2$negative_score)
cor.test(label_emo2$negative_score, label_emo2$swl)

#compute distortion score
dis_score <- aggregate(data.frame(dis_score = label_scale2$distortion == 1), list(userid = label_scale2$userid), sum)
label_emo <- merge(dis_score, label_emo, by = 'userid')

label_emo$distortion_score <- label_emo$dis_score/label_emo$post_count

label_emo$distortion_score2 <- label_emo$dis_score/60
```

```{r}
#remove duplicate the compute correlation
label_emo2 <- label_emo[!duplicated(label_emo$userid),]
cor.test(label_emo2$distortion_score, label_emo2$CESD_sum)
#0.2608511  p-value = 0.02194
cor.test(label_emo2$distortion_score, label_emo2$swl)

cor.test(label_emo2$dis_score, label_emo2$CESD_sum)
#0.299784   p-value = 0.008078
mean(label_emo2$dis_score)
sd(label_emo2$dis_score)
cor.test(label_emo2$dis_score, label_emo2$swl)

label_emo3 <- label_emo2
label_emo3$distortion_score[label_emo3$distortion_score != 0]<- 1
cor.test(label_emo3$distortion_score, label_emo3$CESD_sum)
#0.2790798   p-value = 0.01397  #the presence of distortion matters

l <- subset(label_emo2, label_emo2$distortion_score > 0)
cor.test(l$distortion_score, l$CESD_sum)
#0.1680733    p-value = 0.4118


#compute negative thinking score 
neg_score_W <- aggregate(data.frame(dis_score = label_scale2$negative_thinking == 'W'), list(userid = label_scale2$userid), sum)
neg_score_R <- aggregate(data.frame(dis_score = label_scale2$negative_thinking == 'R'), list(userid = label_scale2$userid), sum)

neg_score <- merge(neg_score_R, neg_score_W, by = 'userid') 
colnames(neg_score) <- c('userid', 'rumination','worry')
neg_score$negative_t_score <- neg_score$rumination + neg_score$worry

label_emo <- merge(neg_score, label_emo, by = 'userid')

label_emo$neg_think_score <- label_emo$negative_t_score/label_emo$post_count
label_emo$neg_think_score2 <- label_emo$negative_t_score/label_emo$post_count

#remove duplicate the compute correlation
label_emo2 <- label_emo[!duplicated(label_emo$userid),]
cor.test(label_emo2$neg_think_score, label_emo2$CESD_sum)
#0.04407639   p-value = 0.7035
cor.test(label_emo2$neg_think_score, label_emo2$swl)

label_emo3 <- label_emo2
label_emo3$neg_think_score[label_emo3$neg_think_score != 0]<- 1
cor.test(label_emo3$negative_t_score, label_emo3$CESD_sum)
#0.1098184 p-value = 0.3417
mean(label_emo3$negative_t_score)
sd(label_emo3$negative_t_score)
cor.test(label_emo3$negative_t_score, label_emo3$swl)

cor.test(label_emo3$distortion_score, label_emo3$neg_think_score)
#0.3612368  p-value = 0.001248

#combine negative emo, distortion and negative thinking
label_emo2$transdiag <-  label_emo2$negative_emo_score2 + label_emo2$distortion_score + label_emo2$neg_think_score
cor.test(label_emo2$transdiag, label_emo2$CESD_sum)



#0.1398212  p-value = 0.2252

##sample characterisitcs
demog <- label_emo2 %>% dplyr::select(post_count,repost, age, ope, con, ext, agr, neu, swl, CESD_sum, negative_t_score, negative_score, dis_score, negative_emo_score3, distortion_score2, neg_think_score2)
summary(demog)
sd(demog$negative_emo_score3)
sd(demog$distortion_score2)
sd(demog$neg_think_score2)

length(labels$negative_emo[labels$negative_emo == 1])
length(labels$negative_emo[labels$negative_emo == 3])
length(labels$distortion[labels$distortion == 1])
length(labels$negative_thinking[labels$negative_thinking == 'R'])
length(labels$negative_thinking[labels$negative_thinking == 'W'])
length(labels$negative_thinking[labels$negative_thinking == 'W'])

demog$age[is.na(demog$age)] <- mean(demog$age, na.rm = TRUE)

high_emo_dist <-  subset(demog, demog$distortion_score2 >= mean(demog$distortion_score2))
low_emo_dist <-  subset(demog, demog$distortion_score2 < mean(demog$distortion_score2))

summary(high_emo_dist)
summary(low_emo_dist)

#graph
layout(matrix(c(1,1,2,3), 2, 2, byrow = TRUE))
hist(demog$negative_score, breaks = 50, xlab = 'number of posts', main = 'distribution of negative emotion')
hist(demog$dis_score, breaks = 50,  xlab = 'number of posts', main = 'distribution of cognitive distortion')
hist(demog$negative_t_score, breaks = 50, xlab = 'number of posts', main = 'distribution of negative thinking')

t.test(high_emo_dist$post_count, low_emo_dist$post_count)  #p-value = 0.0001213
t.test(high_emo$age, low_emo$age) 
layout(matrix(c(1,1,2,3), 2, 2, byrow = TRUE))

hist(demog$age, breaks = 50, xlab = 'age', main = 'age distribution')
skewness(demog$age)
kurtosis(demog$age)
hist(high_emo_dist$age, breaks = 50, xlab = 'age', main = 'high cognitive distortion')
skewness(high_emo_dist$age)
kurtosis(high_emo_dist$age)
hist(low_emo_dist$age, breaks = 50, xlab = 'age', main = 'low cognitive distortion') #mainly young people
skewness(low_emo_dist$age)
kurtosis(low_emo_dist$age)

# age graph
layout(matrix(c(1,1,1,
                2,3,4), nr =2, byrow = T))
plot(density(demog$age), ylim=c(0,0.15), main = 'Age Density Plot', col=c("blue"), xlab ='number of people')
lines(density(high_emo_dist$age),  col=c("red"))
lines(density(low_emo_dist$age), col=c("green"))
legend(40,0.14,c("sample population", "high distortion", "low distortion"), lty=c(1,1), lwd=c(2.5,2.5),col=c("blue","red","green"))

hist(demog$age, breaks = 50, xlab = 'age', col= 'blue',main = 'age distribution')
hist(high_emo_dist$age, breaks = 50, xlab = 'age', col= 'red', main = 'high cognitive distortion')
hist(low_emo_dist$age, breaks = 50, xlab = 'age', col= 'green', main = 'low cognitive distortion') #mainly young people

#t tests of big-5
t.test(high_emo_dist$ope, low_emo_dist$ope) 
hist(high_emo_dist$ope, breaks = 50)
hist(low_emo_dist$ope, breaks = 50) 
t.test(high_emo_dist$con, low_emo_dist$con)
t.test(high_emo_dist$ext, low_emo_dist$ext) #p-value = 0.03094
t.test(high_emo_dist$agr, low_emo_dist$agr)
t.test(high_emo_dist$neu, low_emo_dist$neu)
t.test(high_emo_dist$swl, low_emo_dist$swl)


t.test(high_emo_dist$CESD_sum, low_emo_dist$CESD_sum) # p-value = 0.00783
hist(high_emo_dist$CESD_sum, breaks = 50)
hist(low_emo_dist$CESD_sum, breaks = 50)

par(mfrow=c(3,4)) 
qqnorm(high_emo_dist$CESD_sum, main = 'CESD (high)')
qqline(high_emo_dist$CESD_sum)
qqnorm(low_emo_dist$CESD_sum, main =  'CESD (low)')
qqline(low_emo_dist$CESD_sum)

qqnorm(high_emo_dist$con, main = 'con (high)')
qqline(high_emo_dist$con)
qqnorm(low_emo_dist$con, main =  'con (low)')
qqline(low_emo_dist$con)

qqnorm(high_emo_dist$ext, main = 'ext (high)')
qqline(high_emo_dist$ext)
qqnorm(low_emo_dist$ext, main =  'ext (low)')
qqline(low_emo_dist$ext)

qqnorm(high_emo_dist$agr, main = 'agr (high)')
qqline(high_emo_dist$agr)
qqnorm(low_emo_dist$agr, main =  'agr (low))')
qqline(low_emo_dist$agr)
hist(high_emo_dist$agr, breaks = 50)
hist(low_emo_dist$agr, breaks = 50)

qqnorm(high_emo_dist$neu, main = 'neu(high)')
qqline(high_emo_dist$neu)
qqnorm(low_emo_dist$neu, main =  'neu(low)')
qqline(low_emo_dist$neu)

qqnorm(high_emo_dist$swl, main = 'swl(high)')
qqline(high_emo_dist$swl)
qqnorm(low_emo_dist$swl, main =  'swl(low)')
qqline(low_emo_dist$swl)


mean(high_emo_dist$CESD_sum)
sd(high_emo_dist$CESD_sum)
mean(low_emo_dist$CESD_sum)
sd(low_emo_dist$CESD_sum)


wilcox.test(high_emo_dist$negative_emo_score3, low_emo_dist$negative_emo_score3)
wilcox.test(high_emo_dist$distortion_score2, low_emo_dist$distortion_score2)
wilcox.test(high_emo_dist$neg_think_score2, low_emo_dist$neg_think_score2)

cohen.d(high_emo_dist$post_count, low_emo_dist$post_count)  #p-value = 0.0001213
cohen.d(high_emo_dist$age, low_emo_dist$age) #p-value = 0.04721
cohen.d(high_emo_dist$ope, low_emo_dist$ope) #p-value = 0.04939
cohen.d(high_emo_dist$con, low_emo_dist$con)
cohen.d(high_emo_dist$ext, low_emo_dist$ext) #p-value = 0.01767
cohen.d(high_emo_dist$agr, low_emo_dist$agr)
cohen.d(high_emo_dist$neu, low_emo_dist$neu)
cohen.d(high_emo_dist$swl, low_emo_dist$swl)
cohen.d(high_emo_dist$CESD_sum, low_emo_dist$CESD_sum) #p-value = 0.02463
cohen.d(high_emo_dist$negative_emo_score3, low_emo_dist$negative_emo_score3)
cohen.d(high_emo_dist$distortion_score2, low_emo_dist$distortion_score2)
cohen.d(high_emo_dist$neg_think_score2, low_emo_dist$neg_think_score2)



#regression CESD with 3 predicting variables
fit <- lm(CESD_sum ~ negative_emo_score3 + distortion_score2 + neg_think_score2, data=label_emo2)
summary(fit) 

coefficients(fit) # model coefficients
confint(fit, level=0.95) # CIs for model parameters 
fitted(fit) # predicted values
residuals(fit) # residuals
anova(fit) # anova table 
vcov(fit) # covariance matrix for model parameters 
influence(fit) # regression diagnostics

layout(matrix(c(1,2,3,4),2,2)) # optional 4 graphs/page 
plot(fit)



###demographic info
#assign 'others' to empty ethnicity
label_emo2
label_emo2$ethnicity[label_emo2$ethnicity == ''] <- NA
label_emo2$ethnicity[is.na(label_emo2$ethnicity)] <- 'Others'

#martial information
label_emo2$marital_status[label_emo2$marital_status == ''] <- NA
levels <- levels(label_emo2$marital_status)
levels[length(levels) + 1] <- "Unknown"
label_emo2$marital_status <- factor(label_emo2$marital_status, levels = levels)
label_emo2$marital_status[is.na(label_emo2$marital_status)] <- 'Unknown'

#parents together
label_emo2$parents_together[label_emo2$parents_together == ''] <- NA
label_emo2$parents_together[is.na(label_emo2$parents_together)] <- 'Other'
label_emo2$parents_together[label_emo2$parents_together == 'I am not 21 years old yet'] <- 'Other'
levels <- levels(label_emo2$parents_together)
levels[length(levels) + 1] <- "No\\ but in frequent contact with parents"
label_emo2$parents_together <- factor(label_emo2$parents_together, levels = levels)


label_emo2$parents_together[label_emo2$parents_together == 'No\\ but in frequent contact with non-resident father'] <- 'No\\ but in frequent contact with parents'
label_emo2$parents_together[label_emo2$parents_together == 'No\\ but in frequent contact with non-resident mother'] <- 'No\\ but in frequent contact with parents'

##relationship status convert other -> 5, live with a partner -> in a relationship, engage -> in a relationship
label_emo2$relationship_status[is.na(label_emo2$relationship_status)] <- 5
label_emo2$relationship_status[label_emo2$relationship_status == 0] <- 1
label_emo2$relationship_status[label_emo2$relationship_status == 10] <- 2
label_emo2$relationship_status[label_emo2$relationship_status == 4] <- 2
#######
label_emo2$parents_together <- factor(label_emo2$parents_together)
label_emo2$marital_status <- factor(label_emo2$marital_status)
label_emo2$ethnicity <- factor(label_emo2$ethnicity)
label_emo2$relationship_status <- factor(label_emo2$relationship_status)


table(label_emo2$ethnicity)
table(label_emo2$parents_together)
table(label_emo2$marital_status)
table(label_emo2$gender)
table(label_emo2$relationship_status)

mean(label_emo2$negative_emo_score3)
sd(label_emo2$negative_emo_score3)

mean(label_emo2$distortion_score2)
sd(label_emo2$distortion_score2)

mean(label_emo2$neg_think_score2)
sd(label_emo2$neg_think_score2)

mean(label_emo2$CESD_sum)


##users with divorced and not divorced parents
nf <- subset(label_emo2, label_emo2$parents_together== 'No\\ but in frequent contact with parents')
nf2 <- subset(label_emo2, label_emo2$parents_together!= 'No\\ but in frequent contact with parents')
mean(nf$negative_emo_score3)
sd(nf$negative_emo_score3)

mean(nf$distortion_score2)
sd(nf$distortion_score2)

mean(nf$neg_think_score2)
sd(nf$neg_think_score2)

mean(nf$CESD_sum)

####compared parents separated with not separated

nf <- subset(label_emo2, label_emo2$parents_together== 'Yes')
nf2 <- subset(label_emo2, label_emo2$parents_together!= 'Yes')
nf2 <- subset(nf2, nf2$parents_together!= 'Other')
mean(nf$negative_score)
sd(nf$negative_score)

mean(nf$dis_score)
sd(nf$dis_score)

mean(nf$negative_t_score)
sd(nf$negative_t_score)

mean(nf$CESD_sum)
sd(nf$CESD_sum)

###
mean(nf2$negative_score)
sd(nf$negative_score)

mean(nf2$dis_score)
sd(nf2$dis_score)

mean(nf2$negative_t_score)
sd(nf2$negative_t_score)

mean(nf2$CESD_sum)
sd(nf2$CESD_sum)

###t-test
wilcox.test(nf$negative_score, nf2$negative_score, conf.int=TRUE)
wilcox.test(nf$dis_score, nf2$dis_score , conf.int=TRUE)
wilcox.test(nf$negative_t_score, nf2$negative_t_score, conf.int=TRUE)
wilcox.test(nf$CESD_sum, nf2$CESD_sum , conf.int=TRUE)



###relationship 

nf <- subset(label_emo2, label_emo2$relationship_status== 1 | label_emo2$relationship_status == 2 | label_emo2$relationship_status == 3)

nf1 <- subset(label_emo2, label_emo2$relationship_status== 1)
nf2 <- subset(label_emo2, label_emo2$relationship_status== 2)
nf3 <- subset(label_emo2, label_emo2$relationship_status== 3)

#normality of residual turns out residual is not normal, so we can't use ANOVA because the p value is largely depend on the normality of the residual 
lm.rela <- lm(negative_emo_score3 ~ relationship_status, data = nf)
res1=residuals(lm.rela,type="pearson")
shapiro.test(res1)

#fit.rela <- aov(negative_emo_score3 ~ relationship_status, data = nf)
#summary(fit.rela)
#tuk<- TukeyHSD(fit.rela)

# graph
layout(matrix(c(1,1,2,3), 2, 2, byrow = TRUE))
p1 <- ggplot(nf, aes(x=dis_score, color=relationship_status)) +
  geom_density() 
p1 = p1 + theme(legend.position="none") + labs(x= "cognitive distortion")


p2 <- ggplot(nf, aes(x=negative_t_score, color=relationship_status)) +
  geom_density() 
p2 = p2 + theme(legend.position="none") + labs(x= "negative thinking")


p <- ggplot(nf, aes(x=negative_score, color=relationship_status)) +
  geom_density() 
p = p + theme(legend.position="bottom") + labs(x= "negative emotion") + scale_color_hue(labels = c("single", "relationship", "married"))

kruskal.test(neg_think_score2 ~ relationship_status, data = nf) 
kruskal.test(negative_emo_score3 ~ relationship_status, data = nf) 
kruskal.test(distortion_score2 ~ relationship_status, data = nf) 

require(gridExtra)

gs =list(p1,p2,p)
grid.arrange(grobs=gs,
             layout_matrix = rbind(c(1, 2),
                                   c(3, 3)))



# ###t-test
# wilcox.test(nf$negative_emo_score3, nf2$negative_emo_score3)
# wilcox.test(nf$distortion_score2, nf2$distortion_score2)
# wilcox.test(nf$neg_think_score2, nf2$neg_think_score2)
# wilcox.test(nf$CESD_sum, nf2$CESD_sum)
# 
# nf <- subset(label_emo2, label_emo2$relationship_status== 2)
# nf2 <- subset(label_emo2, label_emo2$relationship_status !=2)
# nf2 <- subset(nf2, nf2$relationship_status != 5) #not other
# 
# mean(nf$negative_emo_score3)
# sd(nf$negative_emo_score3)
# 
# mean(nf$distortion_score2)
# sd(nf$distortion_score2)
# 
# mean(nf$neg_think_score2)
# sd(nf$neg_think_score2)
# 
# mean(nf$CESD_sum)
# 
# 
# #ANOVA
# fit <- aov()
# 
# ###t -test
# t.test(nf$negative_emo_score3, nf2$negative_emo_score3)
# t.test(nf$distortion_score2, nf2$distortion_score2)
# t.test(nf$neg_think_score2, nf2$neg_think_score2)
# t.test(nf$CESD_sum, nf2$CESD_sum)
# 
# 
# 
# nf <- subset(label_emo2, label_emo2$relationship_status== 3)
# nf2 <- subset(label_emo2, label_emo2$relationship_status != 3)
# nf2 <- subset(nf2, nf2$relationship_status != 5) #not other
# 
# mean(nf$negative_emo_score3)
# sd(nf$negative_emo_score3)
# 
# mean(nf$distortion_score2)
# sd(nf$distortion_score2)
# 
# mean(nf$neg_think_score2)
# sd(nf$neg_think_score2)
# 
# mean(nf$CESD_sum)
# ##
# mean(nf2$negative_emo_score3)
# sd(nf2$negative_emo_score3)
# 
# mean(nf2$distortion_score2)
# sd(nf2$distortion_score2)
# 
# mean(nf2$neg_think_score2)
# sd(nf2$neg_think_score2)
# 
# mean(nf2$CESD_sum)
# 
# 
# 
# ###t -test
# wilcox.test(nf$negative_emo_score3, nf2$negative_emo_score3)
# wilcox.test(nf$distortion_score2, nf2$distortion_score2)
# wilcox.test(nf$neg_think_score2, nf2$neg_think_score2)
# wilcox.test(nf$CESD_sum, nf2$CESD_sum)
# 



##gender
nf <- subset(label_emo2, label_emo2$gender== 0)
nf2 <- subset(label_emo2, label_emo2$gender== 1)
mean(nf$negative_emo_score3)
sd(nf$negative_emo_score3)

mean(nf$distortion_score2)
sd(nf$distortion_score2)

mean(nf$neg_think_score2)
sd(nf$neg_think_score2)

mean(nf$CESD_sum)

###t -test
t.test(nf$negative_emo_score3, nf2$negative_emo_score3)
t.test(nf$distortion_score2, nf2$distortion_score2)
t.test(nf$neg_think_score2, nf2$neg_think_score2)
t.test(nf$CESD_sum, nf2$CESD_sum)



l <- subset(label_emo2, marital_status == 'Married with child/children')

###regression CESD with all variables
library(caret)
ethnicity_dummies <- data.frame(predict(dummyVars(~ ethnicity, data = label_emo2), newdata = label_emo2))
marri_dummies <-  data.frame(predict(dummyVars(~ marital_status, data = label_emo2), newdata = label_emo2) %>% .[, -1])
parents_dummies <-  data.frame(predict(dummyVars(~ parents_together, data = label_emo2), newdata = label_emo2))
#label_emo2$relationship_status[is.na(label_emo2$relationship_status)] <- 0
rela_dummies <-  data.frame(predict(dummyVars(~ relationship_status, data = label_emo2), newdata = label_emo2))

###merge all dummies


all_dum <- cbind(ethnicity_dummies, parents_dummies)
all_dum <- cbind(all_dum, marri_dummies)
all_dum <- cbind(all_dum, rela_dummies)

label_emo2$age[is.na(label_emo2$age)] <- mean(label_emo2$age, na.rm = TRUE)
selected <- label_emo2 %>% dplyr::select(negative_emo_score3, distortion_score2, neg_think_score2, gender, age, CESD_sum, post_count)

###for age, assign mean to NA


all_var <- cbind(selected, all_dum)

fit3 <- lm(CESD_sum ~ ., data=all_var)
summary(fit3) 

layout(matrix(c(1,2,3,4),2,2)) # optional 4 graphs/page 
plot(fit3)
coefficients(fit3)


fit2 <- lm(CESD_sum ~ negative_emo_score3 + distortion_score2 + parents_together.Yes + parents_together.No..and.not.in.frequent.contact.with.non.resident.mother
           +relationship_status.3 + marital_status.Married.with.child.children, data=all_var)
summary(fit2)

#Residuals:
#   Min      1Q  Median      3Q     Max 
# -22.231  -6.769  -1.228   8.036  22.932 
# 
# Coefficients:
#   Estimate Std. Error t value Pr(>|t|)    
# (Intercept)                                                                 21.795      3.039   7.171 6.51e-10 ***
#   negative_emo_score2                                                          0.928     15.761   0.059   0.9532    
# distortion_score                                                           139.650     95.563   1.461   0.1485    
# neg_think_score                                                            -26.729     47.338  -0.565   0.5742    
# parents_together.Yes                                                        -5.464      3.136  -1.742   0.0859 .  
# parents_together.No..and.not.in.frequent.contact.with.non.resident.mother   10.248      6.845   1.497   0.1389    
# as.character.relationship_status.1                                           3.092      2.666   1.160   0.2501    
# marital_status.Married.with.child.children                                  12.723      6.751   1.884   0.0637 .  
# ---
#   Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
# 
# Residual standard error: 11.16 on 69 degrees of freedom
# Multiple R-squared:  0.182,	Adjusted R-squared:  0.09902 
# F-statistic: 2.193 on 7 and 69 DF,  p-value: 0.04528


####regression swl
swl_selected <- label_emo2 %>% dplyr::select(negative_emo_score2, distortion_score, neg_think_score, gender, age, swl)
all_var_swl <- cbind(swl_selected, all_dum)

fit_swl <- lm(swl ~ ., data=all_var_swl)
summary(fit_swl) 

layout(matrix(c(1,2,3,4),2,2)) # optional 4 graphs/page 
plot(fit_swl)


####correlation between all variables
all_var <- all_var[order(all_var$negative_emo_score2),]
all_var <- all_var[order(all_var$distortion_score),]
all_var <- all_var[order(all_var$neg_think_score),]

cor_all <- round(cor(all_var),2)

cor_all_matrix <- data.matrix(cor_all)

all_var_heatmap <- heatmap(cor_all_matrix, Rowv=NA, Colv=NA, col = rainbow(12), scale="column", margins=c(5,10))

cor.test(all_var$neg_think_score, all_var$age)


###shows no correlation with value scale 
##time 
time <- as.data.frame(str_split_fixed(labels$post_time, "\\s+", 2))
colnames(time) <- c('date', 'time')

#date2 <- str_split_fixed(time$date, "/", 2)
hour <- str_split_fixed(time$time, ":", 2)
colnames(hour) <- c('hour', 'min')
labels2 <- cbind(labels, hour)
labels2$hour <- as.numeric(as.character(labels2$hour))
labels2$late_night <- 0
labels2$late_night[labels2$hour<=6] <- 1

late_night2 <- aggregate(data.frame(late_count = labels2$late_night == 1), list(userid = labels2$userid), sum)


selected4 <- label_emo2 %>% dplyr::select(userid, negative_emo_score2, negative_score, distortion_score, negative_t_score, neg_think_score, dis_score, gender, age, CESD_sum, post_count, swl)

###for age, assign mean to NA
all_var2 <- cbind(selected4, all_dum)
all_var_time <- merge(late_night2, all_var2,  by='userid')
all_var_time$late_pro <- all_var_time$late_count/ all_var_time$post_count
cor.test(all_var_time$late_pro, all_var_time$negative_emo_score2)
#0.2930801 **

cor.test(all_var_time$late_pro, all_var_time$distortion_score)
#0.2995864 **


cor.test(all_var_time$late_pro, all_var_time$neg_think_score)
#0.2854979*


cor.test(all_var_time$late_count, all_var_time$post_count)
#0.7672654 *** late count is highly correlated with post count



#regression 
fit_dep <- lm(CESD_sum ~ negative_emo_score3 + distortion_score2 + post_count +  late_count + parents_together.Yes + relationship_status.3 + parents_together.No..and.not.in.frequent.contact.with.non.resident.mother 
           + marital_status.Married.with.child.children + parents_together.No..and.not.in.frequent.contact.with.non.resident.mother, data=all_var_time)
summary(fit_dep) 

fit_dist <- lm(distortion_score2 ~   late_count + parents_together.Yes + relationship_status.3 + relationship_status.1 + parents_together.No..and.not.in.frequent.contact.with.non.resident.mother 
               + parents_together.No..but.in.frequent.contact.with.parents , data=all_var_time)
summary(fit_dist) 


#merge with like


##what they like vs what they talk
selected3 <- label_emo2 %>% dplyr::select(userid, negative_emo_score2, distortion_score, neg_think_score, CESD_sum)
user_like <- read.csv("status_dep_demog_big5_schwartz_swl_like.csv", header = T, fill=TRUE,row.names=NULL)%>% dplyr::select(userid, like_id)
user_like_s <- merge(selected3, user_like, by = 'userid')

###high CES_D group 24-60: Severe depressive symptomatology
high_cesd <- subset(user_like_s, user_like_s$CESD_sum >24)

##high CES_D group  like frequency 
like_list_h <- unlist(strsplit(as.character(high_cesd$like_id), "[,]"))
freq_like_h<-table(like_list_h)
freq_like1_h <-sort(freq_like_h, decreasing=TRUE)
like.sorted.table_h<-paste(names(freq_like1_h), freq_like1_h, sep="\\t")
head(like.sorted.table_h, n=50)


###low CES_D 0-16: No to mild depressive symptomatology
low_cesd <- subset(user_like_s, user_like_s$CESD_sum <16)

###correlation of like with variables 
require(tm)
c <- VCorpus(VectorSource(user_like_s$like_id))
freq <- as.data.frame(as.matrix(DocumentTermMatrix(c)))

#with CESD
CESD <- label_emo2%>% dplyr::select(userid, CESD_sum)
all <- cbind(CESD, freq)
v <- as.data.frame(t(round(cor(all$CESD_sum, all[3:25873]),2)))
#like <- as.data.frame(str_split_fixed(v$V1, "\\s+", 2))
v1 <- cbind(like_id = rownames(v), v) 
colnames(v1) <- c('like_id', 'cor.CESD')
top10_dep <- as.data.frame(with(v1, v1[order(cor.CESD), ]))[1:10,]
top10_dep2 <- as.data.frame(with(v1, v1[order(-cor.CESD), ]))[1:10,]

#with negative emotion
neg_emo <- label_emo2%>% dplyr::select(userid, negative_emo_score3)
all2 <- cbind(neg_emo, freq)
v <- as.data.frame(t(round(cor(all2$negative_emo_score3, all2[3:25873]),2)))
#like <- as.data.frame(str_split_fixed(v$V1, "\\s+", 2))
v1 <- cbind(like_id = rownames(v), v) 
colnames(v1) <- c('like_id', 'cor.negEmo')
top10_neg <- as.data.frame(with(v1, v1[order(cor.negEmo), ]))[1:10,]
top100_neg2 <- as.data.frame(with(v1, v1[order(-cor.negEmo), ]))[1:100,]
write.csv(top100_neg2, 'top100_neg_like.csv')

#with distortion
dist <- label_emo2%>% dplyr::select(userid, distortion_score2)
all3 <- cbind(dist, freq)
v <- as.data.frame(t(round(cor(all3$dist, all3[3:25873]),2)))
#like <- as.data.frame(str_split_fixed(v$V1, "\\s+", 2))
v1 <- cbind(like_id = rownames(v), v) 
colnames(v1) <- c('like_id', 'cor.dist')
top10_dist <- as.data.frame(with(v1, v1[order(cor.dist), ]))[1:10,]
top100_dist <- as.data.frame(with(v1, v1[order(-cor.dist), ]))[1:100,]
write.csv(top100_dist, 'top100_distortion_like.csv')

#regression with likes this model behave very bizzare !!
all_like <- cbind(all_var_time, freq)

fit_dist <- lm(distortion_score2 ~  late_count + parents_together.Yes + relationship_status.3 + parents_together.No..and.not.in.frequent.contact.with.non.resident.mother 
               + marital_status.Married.with.child.children + parents_together.No..and.not.in.frequent.contact.with.non.resident.mother + fea1 + fea3 + fea4 + fea5 + fea6 , data=all_like)
summary(fit_dist) 



all_like$fea1  <- all_like$'2b493afba3cff3b5dece55fa1849bf25,'
all_like$fea2  <- all_like$'5d54993bcf9a1f1a4077ab73e07e7371,'
all_like$fea3  <- all_like$'42a1dd271a4b7352e6b51346c2b66c9f,'
all_like$fea4  <- all_like$'0259db20a2050363db3aaccbfd9f512b,'
all_like$fea5  <- all_like$'48ed827674de61ea0ed3e1ba01e6d171,'
all_like$fea6  <- all_like$'eebf5857fdd07b21a97262015ec333c5,'






##frequency table
like_list_l <- unlist(strsplit(as.character(low_cesd$like_id), "[,]"))
freq_like_l<-table(like_list_l)
freq_like1_l <-sort(freq_like_l, decreasing=TRUE)
like.sorted.table_l<-paste(names(freq_like1_l), freq_like1_l, sep="\\t")
head(like.sorted.table_l, n=50)

##high transdiagnostics symptoms
high_emo_like <- subset(user_like_s, user_like_s$negative_emo_score2 >= mean(user_like_s$negative_emo_score2))
high_emo_dist2 <- subset(high_emo_like, high_emo_like$distortion_score >= mean(user_like_s$distortion_score))

like_list_h2 <- unlist(strsplit(as.character(high_emo_dist2$like_id), "[,]"))
freq_like_h2<-table(like_list_h2)
freq_like1_h2 <-sort(freq_like_h2, decreasing=TRUE)
like.sorted.table_h2<-paste(names(freq_like1_h2), freq_like1_h, sep="\\t")
head(like.sorted.table_h2, n=50)

#low transdiagnostics symptoms
low_emo_like <- subset(user_like_s, user_like_s$negative_emo_score2 < mean(user_like_s$negative_emo_score2))
low_emo_dist2 <- subset(low_emo_like, low_emo_like$distortion_score < mean(user_like_s$distortion_score))

like_list_l2 <- unlist(strsplit(as.character(low_emo_dist2$like_id), "[,]"))
freq_like_l2<-table(like_list_l2)
freq_like1_l2 <-sort(freq_like_l2, decreasing=TRUE)
like.sorted.table_l2<-paste(names(freq_like1_l2), freq_like1_l2, sep="\\t")
head(like.sorted.table_l2, n=50)

####LIWC

liwc <- read.csv("LIWC_resample_5000.csv", header = T, fill=TRUE,row.names=NULL) 
liwc$text <- NULL   
liwc2 <- liwc  
liwc2[2:93] <- scale(liwc[2:93])

liwc_sum <- aggregate(data.frame(sum_score = liwc2[,2:93]), list(userid = liwc2$userid), sum)
                        
liwc_sum <- liwc_sum[-1,]


CESD <- all_var_time %>% dplyr::select(userid, CESD_sum, negative_score, dis_score, negative_t_score, parents_together.Yes, relationship_status.3, late_pro )
liwc_CESD <- merge(CESD, liwc_sum, by='userid')
cor_dist <- t(cor(liwc_CESD$negative_score, liwc_CESD[2:100]))
cor_dist2 <- t(cor(liwc_CESD$dis_score, liwc_CESD[2:100]))
cor_dist3 <- t(cor(liwc_CESD$negative_t_score, liwc_CESD[2:100]))




#dist <- label_emo2 %>% dplyr::select(userid, distortion_score)
#liwc_dist <- merge(dist, liwc_day, by='userid')


fit_dist <- lm(dis_score ~ 
               +  sum_score.pronoun 
               + sum_score.shehe+ sum_score.prep
               + sum_score.swear
               + sum_score.feel+ sum_score.reward+ sum_score.risk +late_pro, data=liwc_CESD)
summary(fit_dist)

c <- cor(round(liwc_CESD[11:100]))

write.csv(c, "liwc_cor.csv")







```
