---
title: "Thoughts On CSCW Paper"
author: "Maria Wolters"
date: "11 3 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
require(tidyverse)
require(lubridate)

```

User_scale_post_time2.csv consist of `r length(userinfo)` users of the myPersonality app. These users completed the CESD scale, big-5 personality test, Schwartz value scale, satisfaction with life scale. We also have their demographic information 

```{r load-data}
setwd('~/phd_work/mypersonality_data/cognitive_distortion/')

post_cutoff <- 0.3
userinfo <- read.csv("./data/user_scale_post_time2.csv")



userinfo$postfreq <- userinfo$post_count / userinfo$date_spread

userinfo$regular <- ifelse(userinfo$postfreq > post_cutoff,1,0) 


userinfo$last_date_ld <-  ymd(userinfo$last_date)

userinfo$first_date_ld <-  ymd(userinfo$earliest_date)

userinfo$date_added_CESD_ld <- ymd_hms(userinfo$date_added_CESD)

userinfo$CESD_lastdate <- as.duration(interval(userinfo$last_date_ld,userinfo$date_added_CESD_ld))

userinfo$CESD_firstdate <- interval(userinfo$first_date_ld,userinfo$date_added_CESD_ld)

# is the last post after the person completed the CES-D?
userinfo$last_post_after_CESD <- userinfo$last_date_ld > date(userinfo$date_added_CESD_ld)

# is the last post in the week before the person completed the CES-D or later?
userinfo$last_post_week_CESD <- (userinfo$last_date_ld - date(userinfo$date_added_CESD_ld)) > -7


regusers <- subset(userinfo,userinfo$regular==1)

nreg <- nrow(regusers)

nuser <- nrow(userinfo)



```


## Research Questions

1. To what extent do transdiagnostic features, such as frequency of negative thoughts, correlate with variables that have often been used as ground truth in mental health and social media?  
2. Are there any relevant differences between users that use FB often enough to allow longitudinal analysis and those who do not?  

## Rationale for Sampling Strategy 

We want to ensure that we sample from people with a range of depression scores and a range of personalities that have enough data to create meaningful user profiles - this means that we need people with full questionnaire data and people who regularly post on Facebook. The original set consists of  `r I(nuser)` people. 

For our purposes, we define regular posters as people who post twice per week or more. We estimate this using the average post count per day during the sampling frame. If this is `r I(post_cutoff)`, that means that people make around `r I(365*post_cutoff)` posts in 365 days, which is roughly equivalent to an average of `r I(365/52*post_cutoff)`  posts per week. The number of regular users is `r I(nreg)`. 

If the column date_added_CESD is the day on which people completed the CES-D questionnaire, then we know which posts are from the time period that is reflected in the CES-D score. Since the CES-D score provides us with a ground truth, we analyse data from posts that have been made around the time that the score was obtained. 

Looking at the distribution of the posts for our regular users, we find the following:

```{r regular-cesd}

knitr::kable(table(userinfo$regular,userinfo$last_post_week_CESD),caption="1 - regular users, TRUE - last post less than a week before CES-D taken or later")

knitr::kable(table(userinfo$regular,userinfo$last_post_after_CESD),caption="1 - regular users, TRUE - last post after CES-D was taken")


forAnalysis <- subset(regusers, regusers$last_post_week_CESD==1)

```

To ensure a sufficiently large data set for potential automatic classification, we choose to include those `r I(nrow(forAnalysis))` users whose last post is less than a week before their CES-D posts, and label *all posts made in the two months before CES-D was recorded* for the presence of our transdiagnostic criteria, negative thoughts and cognitive distortion. This ensures that we use the same sampling frame for every user. If we restrict ourselves to users who were active both before and after they took the CES-D, then this would leave only `r I(as.numeric(table(regusers$last_post_after_CESD)[2]))` users for analysis. 

The data set specifying the users for whom posts should be annotated is stored in the file users_to_be_analysed.csv, which is generated automatically by this script. 

LC labels all extracted posts, MW checks all cognitive distortion posts and a sample of 10% of all negative thoughts posts, and a psychologist cross checks all cognitive distortion posts.

WM and MW check all posts in the data set by all `r I(nrow(forAnalysis))` users for mentions of a mental health diagnosis (WM: uses technique from de Choudhury papers, MW: close reading of all users where keyword spotting did not yield a diagnosis)


```{r write-included}
write.csv(forAnalysis,"users_to_be_analysed.csv")
```

## Research Question 1: Correlation with Transdiagnostic Features

Target variables: 

1. does the person report a diagnosis of a mental health problem? 
2. CES-D score 

Transdiagnostic variables:

1. negative thoughts (will be more frequent)
2. cognitive distortion (will be much rarer)

Control variables: demographics, personality, satisfaction with life 

Analysis techniques: Logistic regression models. Classifiers _only after_ the models have been created and interpreted. 

We are not interested in the correlation between negative thoughts / cognitive distortions and psychopathology, we are interested in the correlation between _visible, publicly stated_ negative thoughts and psychopathology. We are especially interested in those people who talk about a mental health problem, or score highly on the CES-D, but who show no evidence of negative thoughts or cognitive distortions in their posts.  

## Research Question 2: Differences Between Users in / outside of Sample 

Statistical analysis and characterisation of users included in our sample, comparison with users excluded from our sample. We need to check whether there are any systematic differences in depression scores, personality, and values. This contributes to the discussion of the extent to which people disclosed their mental health problems on FB. This is the kind of critical interrogation that's appropriate for CSCW. 



